The Impact of Extreme Weather Events on Property Insurance Pricing

### 2023-10-31 manuscript/manuscript.tex
modify bib

% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

While previous research has examined different aspects of this complex issue, including the impact of weather risks on insurance 
prices, there is much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
\cite{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
understanding of how frequency and severity affect the pricing of property insurance. We are also trying to identify effective 
strategies that can reduce the financial burden of homeowners in the face of these major disasters.

This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
data from reliable sources, such as the Insurance Information Agency, National Centers for Environmental Informations, and Aon's 2023 
Weather, Climate and Disaster Investigation Report. This study is not only timely but critically important at a time of increasing 
weather-related risks, with the goal of contributing to homeowner well-being and the stability of the property insurance market.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\linewidth]{NCEI US disaster freq.pdf}
    \caption{}
    \label{fig:disaster_freq}
\end{figure}

@@

\bibliography{refs}
\bibliographystyle{chicago}

>>>>

% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage[style=numeric-comp]{biblatex}

@@

While previous research has examined different aspects of this complex issue, including the impact of weather risks on insurance 
prices, there is much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
\citep{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
understanding of how frequency and severity affect the pricing of property insurance. We are also trying to identify effective 
strategies that can reduce the financial burden of homeowners in the face of these major disasters.

This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
data from reliable sources, such as the Insurance Information Agency, NationalInsurance Centers for Environmental Informations, and Aon's 2023 
Weather, Climate and Disaster Investigation Report. This study is not only timely but critically important at a time of increasing 
weather-related risks, with the goal of contributing to homeowner well-being and the stability of the property insurance market.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\linewidth]{NCEI US disaster freq.pdf}
    \label{fig:disaster_freq}
\end{figure}

@@

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}
